\Title

### 2024-06-18 source/tex/paper.tex
Correct syntax errors on ::LaTeXForm and ::Indices for Cadabra 2.5.2
Prior to version 2.5.2 Cadabra would allow LaTeXForm{"foo"} but since 2.5.2 must use round brackets. Also, since 2.5.2, cannot have whitespace between ::Indices and the round brackets, must use ::Indices(foo). Ditto for other properties (e.g., LaTeXForm("foo")). These were errors on my part that earlier versions of Cadabra let slip through. But 2.5.2 closes these loopholes.

% ============================================================================================
\title{\Title}
\author{\Author\\[10pt]%
School of Mathematics\\%
Monash University, 3800\\%
Australia}
% \date{10-Nov-2008}% 1st version started
% \date{29-Nov-2008}% 1st version finished
% \date{10-Mar-2009}% 1st version to gr-qc
% \date{22-Mar-2009}% minor corrections to section 8.2
% \date{09-Jul-2009}% minor grammatical corrections in response to 1st referee
% \date{12-Aug-2009}% small corrections arising from proofs received from CQG
\date{12-Aug-2009 (v1)\\
      10-Dec-2019 (v2)\\  % major changes to correct errors in 4th and higher order terms,
                          % all code will be available on github
       4-Nov-2022 (v3)\\  % corrected typos on lhs of eqtns 11.19a-d,
       1-Dec-2022 (v4)\\  % corrected typo on equation (3.2) in section (3.1)
      21-Nov-2023 (v5)}   % reformatted Cadabra ouput to print \Delta x rather than Dx
\reference{Preprint: arXiv:0903.2087\\[5pt]
           Journal: {\it Class.Quantum.Grav.} {\bf 26} 175017 (2009)}

>>>>

% ============================================================================================
\title{\Title}
\author{\Author\\[10pt]%
School of Mathematics\\%
Monash University, 3800\\%
Australia}
% \date{10-Nov-2008}% 1st version started
% \date{29-Nov-2008}% 1st version finished
% \date{10-Mar-2009}% 1st version to gr-qc
% \date{22-Mar-2009}% minor corrections to section 8.2
% \date{09-Jul-2009}% minor grammatical corrections in response to 1st referee
% \date{12-Aug-2009}% small corrections arising from proofs received from CQG
\date{12-Aug-2009 (v1)\\
      10-Dec-2019 (v2)\\  % major changes to correct errors in 4th and higher order terms,
                          % all code will be available on github
       4-Nov-2022 (v3)\\  % corrected typos on lhs of eqtns 11.19a-d,
       1-Dec-2022 (v4)\\  % corrected typo on equation (3.2) in section (3.1)
      21-Nov-2023 (v5)\\  % reformatted Cadabra ouput to print \Delta x rather than Dx
      24-May-2024 (v6)}   % reinstated equations for generalised connection in section 7,
                          % this matches section 7 of version 1
\reference{Preprint: arXiv:0903.2087\\[5pt]
           Journal: {\it Class.Quantum.Grav.} {\bf 26} 175017 (2009)}
